---
title: "04c_gene_expression_analysis- dds3:  ~ R_treat_TP_final"
author: "Natalia Andrade Rodriguez"
date: "2023-03-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Gene expression analysis for all samples with at least 4M of mapped reads

###Library installing/loading
```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("DESeq2")
library(DESeq2)
library(ggplot2)
library(ggrepel)
library(dplyr)
library(tidyr)
library(reshape2)
library(tidyverse)
```

```{r}
samples_selected_4M<- read.csv("data/samples_selected_4M.csv")

sample_data_pe_ee<- samples_selected_4M %>% 
  
              mutate(colnames = Sample_ID) %>% 
  
              full_join(colnames_countData_4M, by = 'colnames') %>% 
  
              mutate(Geno_R_TP = paste(Genotype,R_TP, sep="_" )) %>%
  
              mutate(Geno_T = paste(Genotype,Treatment, sep="_" )) %>%
  
              mutate(Treat_R_TP = paste(Treatment,R_TP, sep="_" )) %>%
  
              mutate(Geno_R_treat = paste(Genotype,R_treat, sep="_" )) %>%
   
              mutate(R_treat_R_TP = paste(R_treat,R_TP, sep="_" )) %>%

              mutate(R_treat_TP_final = paste(R_treat,R_TP,R_final_state ,sep="_" )) %>%
  
              filter(grepl( "PE|EE" , R_TP)) %>% 
  
              filter(!grepl("PEE", R_TP)) %>% 
  
              filter(!grepl( "2_432" , Sample_ID)) %>% 
  
              #filter(grepl("TRUE", D_PE_D_EE)) %>% 
  
              arrange(order)

samples_pe_ee<- sample_data_pe_ee$Sample_ID  
#96 samples   
sample_data_pe_ee$Genotype_Micro<- as.factor(sample_data_pe_ee$Genotype_Micro)  
sample_data_pe_ee$R_TP<- as.factor(sample_data_pe_ee$R_TP)

row.names(sample_data_pe_ee)<- sample_data_pe_ee$Sample_ID
```


```{r}
countData_4M_pe_ee<- readRDS("data/countData_4M.rds") %>% 
  
               select("2_10","2_100","2_125","2_13","2_132","2_137","2_145","2_15","2_151","2_155","2_158","2_168",
                      "2_170","2_173","2_181","2_19","2_21","2_24","2_248","2_25","2_263","2_276","2_278","2_280","2_289",
                      "2_295","2_3","2_307","2_317","2_32","2_336","2_34","2_344","2_346","2_348","2_350","2_353","2_354",
                      "2_356","2_369","2_37","2_370","2_371","2_372","2_374","2_375","2_379","2_381","2_384","2_389","2_39",
                      "2_390","2_393","2_398","2_4","2_400","2_402","2_405","2_409","2_410","2_411","2_415","2_419","2_420",
                      "2_423","2_424","2_427","2_429","2_43","2_44","2_46","2_47","2_5","2_50","2_56","2_59","2_62",
                      "2_65","2_68","2_69","2_7","2_70","2_73","2_77","2_80","2_81","2_83","2_84","2_85","2_86","2_88","2_9",
                      "2_90","2_91","2_95")

colnames_countData_4M_pe_ee<- as.data.frame(colnames(countData_4M_pe_ee)) %>%
  
                               dplyr::rename('colnames'='colnames(countData_4M_pe_ee)') %>% mutate(order = 1:95)
```


```{r}
keep <-countData_4M_pe_ee %>% mutate(keep = rowSums(countData_4M_pe_ee) >= 200)

countData_4M_pe_ee<- keep %>% filter(keep == TRUE) %>% dplyr::select(-keep)

colnames(countData_4M_pe_ee) == rownames(sample_data_pe_ee)
```
## dds3--> model design :  ~ R_treat_TP_final
```{r}
dds3 = DESeqDataSetFromMatrix(countData = countData_4M_pe_ee, 
                            
                                colData = sample_data_pe_ee, 
 
                                design = ~ R_treat_TP_final)


```

#Analysising DEG
```{r}
if (file.exists("cache/dds3.rds")) {
  dds3<- read_rds("cache/dds3.rds")
} else {
  dds3<- DESeq(dds3)
  write_rds(dds3,"cache/dds3.rds")
}
```

```{r}
vsd3 = vst(dds3, blind = FALSE)
```


#Plots for dds3 ~ R_treat_TP_final
```{r}
pcaData3 = plotPCA(vsd3, intgroup=c("R_TP", "Genotype","Sample_ID", "R_final_state"), 
returnData=TRUE)
percentVar3 = round(100 * attr(pcaData3, "percentVar"))

png("results/PCA_dds3_vst.png", width=7, height=7, units = "in", res = 300)
ggplot(pcaData3, aes(PC1, PC2, colour = R_TP, shape = R_final_state)) + 
geom_point(size = 2) + theme_bw() + 
geom_text_repel(aes(label = Sample_ID), nudge_x = -1, nudge_y = 0.2, size = 3) +
ggtitle("Principal Component Analysis dds3 vst", subtitle = "~ R_treat_TP_final") +
xlab(paste0("PC1: ",percentVar3[1],"% variance")) +
ylab(paste0("PC2: ",percentVar3[2],"% variance"))
dev.off()

#Dispersion plot
png("results/qc-dispersions_dds3.png", 1000, 1000, pointsize=20)
plotDispEsts(dds3, main="Dispersion plot ~ R_treat_TP_final")
dev.off()

#Cook’s distance
png("results/cookdistance_dds3.png", width=15, height=10, units = "in", res = 300)
boxplot_dds3<-boxplot(log10(assays(dds3)[["cooks"]]), range=0, las=0,  main="Cook's distance  ~ R_treat_TP_final")
dev.off()
``` 

#transform data with rlogTransformation
```{r}
rld3 <- rlogTransformation(dds3)
```

```{r}
pcaData3r = plotPCA(rld3, intgroup=c("R_TP", "Genotype","Sample_ID", "R_final_state"), 
returnData=TRUE)
percentVar3r = round(100 * attr(pcaData3r, "percentVar"))

png("results/PCA_dds3_rld.png", width=7, height=7, units = "in", res = 300)
ggplot(pcaData3r, aes(PC1, PC2, colour = R_TP, shape = R_final_state)) + 
geom_point(size = 2) + theme_bw() + 
geom_text_repel(aes(label = Sample_ID), nudge_x = -1, nudge_y = 0.2, size = 3) +
ggtitle("Principal Component Analysis dds3 rld", subtitle = " ~ R_treat_TP_final") +
xlab(paste0("PC1: ",percentVar3r[1],"% variance")) +
ylab(paste0("PC2: ",percentVar3r[2],"% variance"))
dev.off()

```

```{r}
png("results/hist_rld_dds3.png", 1000, 1000, pointsize=20)
hist(assay(rld3))
dev.off()
```

```{r}
resultsNames(dds3)
res_dds3<- results(dds3)
summary(res_dds3)
#attr(dds3, "modelMatrix")
```
We will use contrast to compare our different time point
###1: result we will compare 'C_PE_Healthy',"D_PE_Healthy"
```{r}
res_dds3_1<- results(dds3,contrast =
                                        
                            c("R_treat_TP_final",'C_EE_Healthy',"D_EE_Healthy"))

resOrd_dds3_1<- as.data.frame(res_dds3_1[order(res_dds3_1$padj),])
                
resOrd_dds3_1<- resOrd_dds3_1 %>%  
  
                 mutate(ofav_gene = rownames(resOrd_dds3_1)) %>%
  
                 mutate(contrast = 1) %>% 
                 
                 mutate(contrast_gene = paste(contrast, ofav_gene, sep = "_")) %>% 
   
                 filter(padj<0.1)
```

###2: result we will compare 'D_EE_Diseased',"D_EE_Healthy"
```{r}
res_dds3_2<- results(dds3,contrast =
                                        
                            c("R_treat_TP_final",'D_EE_Diseased',"D_EE_Healthy"))

resOrd_dds3_2<- as.data.frame(res_dds3_2[order(res_dds3_2$padj),])
                
resOrd_dds3_2<- resOrd_dds3_2 %>%  
  
                 mutate(ofav_gene = rownames(resOrd_dds3_2)) %>%
  
                 mutate(contrast = 2) %>% 
                 
                 mutate(contrast_gene = paste(contrast, ofav_gene, sep = "_")) %>% 
   
                 filter(padj<0.1)
```

###3: result we will compare 'C_PE_Diseased',"D_EE_Diseased"
```{r}
res_dds3_3<- results(dds3,contrast =
                                        
                            c("R_treat_TP_final",'C_PE_Diseased',"D_EE_Diseased"))

resOrd_dds3_3<- as.data.frame(res_dds3_3[order(res_dds3_3$padj),])
                
resOrd_dds3_3<- resOrd_dds3_3 %>%  
  
                 mutate(ofav_gene = rownames(resOrd_dds3_3)) %>%
 
                 mutate(contrast = 3) %>% 
                 
                 mutate(contrast_gene = paste(contrast, ofav_gene, sep = "_")) %>% 
   
                 filter(padj<0.1)
```

###4: result we will compare 'C_EE_Healthy',"C_PE_Healthy
```{r}
res_dds3_4<- results(dds3,contrast =
                                        
                            c("R_treat_TP_final",'C_EE_Healthy',"C_PE_Healthy"))

resOrd_dds3_4<- as.data.frame(res_dds3_4[order(res_dds3_4$padj),])
                
resOrd_dds3_4<- resOrd_dds3_4 %>%  
  
                 mutate(ofav_gene = rownames(resOrd_dds3_4)) %>%
  
                 mutate(contrast = 4) %>% 
                 
                 mutate(contrast_gene = paste(contrast, ofav_gene, sep = "_")) %>% 
   
                 filter(padj<0.1)
```


###Merging all the list and adding annotations
```{r}
#Getting gene descriptions found with g:profiler

gene_anno<- read.csv("data/DEG_gprofiler.csv") %>% 

            mutate(contrast_gene = paste(contrast, ofav_gene, sep = "_")) %>% 
  
            select(-contrast, -ofav_gene)
#Binding results for all contrast

resOrd_dds3_all<- rbind(resOrd_dds3_1,resOrd_dds3_2) %>% 
  
                   rbind(resOrd_dds3_3,resOrd_dds3_4)

#Merging expression with annotations

DEG_all_dds3<- resOrd_dds3_all %>% full_join(gene_anno, by="contrast_gene")

write.csv(DEG_all_dds3, "data/DEG_all_anno.csv")
```

